surfing

### 2021-05-10 inst/surfing.Rmd
further work on issue #94

```{r}
players <- read.table("players.txt",header=TRUE)
head(players)
table(players$nation)
players$name
wildcards <- players$name[-(1:36)]
wildcards
```

@@

@@

```{r,label=savesurfiningingdataset}
save(surfing,surfing_maxp,file="surfing.rda")
```

>>>>

```{r}
surfing_table <- read.table("wct_surfers_table.txt",header=TRUE)
head(surfing_table)
table(surfing_table$nation)
surfing_table$name
wildcards <- rownames(surfing_table)[-(1:36)]
wildcards
```

@@

Now compare the finishing order based on points vs the finishing order
on likelhood:

```{r ordertransplotplot,fig.cap="Official ranks vs likelihood rank, WCT"}
 rL <- sort(surfing_maxp,decreasing=TRUE)
 rL[] <- seq_along(rL)
 rO <- seq_len(nrow(surfing_table))
 names(rO) <- rownames(surfing_table)
 rO
 rL

# ordertransplot(rO,rL,xlab="offical rank",ylab="likelihood rank",main="WCT 2019")
```

@@

```{r,label=savesurfiningingdataset}
save(surfing,surfing_maxp,surfing_table,file="surfing.rda")
```
